HPC--101\\Onboarding

### 2019-06-13 hpc_101/sections/01_intro.tex
corrections

  \begin{block}{Online docuements \& FAQ}
    Users are encouraged to look through the online documentation \& FAQ prior to contacting ITS-CI directly.  Many questions we receive are repeated questions and we try to capture them in our FAQ~\\
    \href{https://www.hawaii.edu/its/ci/xcat/}{xCAT cluster information, policies \& FAQ}
  \end{block}
  \begin{block}{Contact Information}
    If your questions is not answered in our online documentation, please contact us at: UH-HPC-Help@lists.hawaii.edu

>>>>

  \begin{block}{Online documents \& FAQ}
    Users are encouraged to look through the online documentation \& FAQ prior to contacting ITS-CI directly.  Many questions we receive are repeat questions and we try to capture them in our FAQ~\\
    \href{https://www.hawaii.edu/its/ci/xcat/}{xCAT cluster information, policies \& FAQ}
  \end{block}
  \begin{block}{Contact Information}
    If your question is not answered in our online documentation, please contact us at: UH-HPC-Help@lists.hawaii.edu
